\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

\begin{textblock}{25}(70,21)
\color{date}\fontspec[Path = fonts/raleway/]{Raleway-ExtraLight}\fontsize{8pt}{10pt}\selectfont
\today
\end{textblock}

\namesection{}{Risyanggi Azmi Faizin}{ % Your name
% \urlstyle{same}\url{http://linkedin.com/in/rafgugi} \\ % Your website, LinkedIn profile or other web address
\href{mailto:risyanggi@gmail.com}{risyanggi@gmail.com} | +62-812-5251-2771 % Your contact information
}

\begin{minipage}[t]{0.08\textwidth} % create a margin
\ 
\end{minipage}
\hfill

\begin{minipage}[t]{0.7\textwidth}

\sectionspace
\sectionspace
\sectionspace
\descript{HR Department, Grab Pte. Ltd.}
\location{28 Sin Ming Lane, \\
\#01-143, Midview City \\
Singapore 573972}
\sectionspace
\sectionspace
\sectionspace

Dear Sir or Maddam,
\sectionspace

I wish to apply for a \textbf{Database Engineer} position in Grab Pte. Ltd. I will have completed my master degree study on Computer Engineering at Institut Teknologi Sepuluh Nopember Surabaya by July 2018 and will be graduated on September 2018. Right now I'm doing my research paper and wish to publish at \textit{Journal of Theoretical and Applied Information Technology}.\sectionspace

I am very coopearative when working in group and able to lead group. I manage conflicts by focus on solution. I am adept at database, backend, and frontend programming with many kinds of architecture. I am enthusiast to learn new things, have experienced in coding with several programming language and very good at C/C++, SQL, Java, and PHP. In addition, competitive programming competition during my study at ITS allowed me to develop my skill in problem solving and algorithm.
\sectionspace

For evaluation, I have enclosed my \textbf{Curriculum Vitæ} including my educational background, expertise, experience, and my researches. I am looking forward to develop my skills in a more challenging work environment at your company. I also welcome the potential growth for future advancement, which can benefit both me and your company.
\sectionspace

Thank you for your time and consideration. I hope to hear from you soon via email at risyanggi[at]gmail.com.\sectionspace

\sectionspace
\sectionspace
\sectionspace
\sectionspace
\sectionspace

Yours faithfully,
\sectionspace
\sectionspace
\sectionspace

Risyanggi Azmi Faizin
\end{minipage} % The end of the right column

\end{document}