\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\renewcommand{\baselinestretch}{1.14}

\begin{document}

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

% \lastupdated

\namesection{}{Risyanggi Azmi Faizin}{ % Your name
% \urlstyle{same}\url{http://linkedin.com/in/rafgugi} \\ % Your website, LinkedIn profile or other web address
\href{mailto:risyanggi@gmail.com}{risyanggi@gmail.com} | +62 812-5251-2771 % Your contact information
}

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection[ITS]{Institut Teknologi\\Sepuluh Nopember}

\descript{Master in Computer Science}
\location{Aug 2016 — Sep 2018 (Expected)}
Conc. in Algorithm \\
\location{GPA: 3.67 / 4.0}
\sectionspace

\descript{BS in Computer Science}
\location{Aug 2012 — Sep 2016}
Conc. in Software and Algorithm \\
\location{GPA: 3.7 / 4.0}
\sectionspace

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}

Github:// \href{https://github.com/rafgugi}{\bf rafgugi} \\
LinkedIn:// \href{https://www.linkedin.com/in/rafgugi}{\bf rafgugi} \\
Instagram:// \href{https://instagram.com/rafgugi}{\bf @rafgugi} \\
\sectionspace

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}
Mobile Computing \\
Computational Intelligence \\
Design of Algorithm \\
Distributed Systems \\
\sectionspace

\subsection{Undergraduate}
Database Management \\
Big Data \\
Design and Analysis of Algorithm \\
Software Design and Architecture \\
Software Project Management \\
Operational Research \\
{\footnotesize \textit{\textbf{(Teaching Assistance) }}} \\
Computer Network \\
Operating System \\
Data Structure
\sectionspace

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\location{Advanced:}
SQL \textbullet{} \LaTeX\ \textbullet{} Ruby \textbullet{} Go \textbullet{} Regex \\
C/C++ \textbullet{} JavaScript \textbullet{} PHP \\
Java \textbullet{} MongoDB \\
\location{Intermediate:}
Python \textbullet{} NodeJS \textbullet{} ReactJS \textbullet{} C\# \\
\location{Familiar:}
Android \textbullet{} Shell \textbullet{} Network
\sectionspace

%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%----------------------------------------------------------------------------------------

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects as Freelancer}

\runsubsection{Aisyiyah Hospital Management System}
\descript{| Programmer}
\location{Dec 2016 – Jul 2017, Padang}
\location{Dec 2019 – Present, Jakarta}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item This hospital previosly did all hospital procedures manually, with books.
\item This web application is actively used with rate of patiens around 100 per day.
\item Using MySQL database, PHP Laravel as backend, and Bootstrap as frontend.
\item I handled the database and the data flows.
\item I currently develop connection with Social Security Administrator for Health, a goverment agency under Ministry of Health.
\end{tightitemize}
\sectionspace

\runsubsection{E-Procurement Semen Indonesia}
\descript{| Lead Programmer}
\location{Sep 2015 – Jun 2016, Gresik}
\begin{tightitemize}
\item This is my very complex system I have done, integrating 3 companies which are Semen Padang, Semen Tonasa, and Semen Indonesia itself.
\item Do procurement and real-time auction, between companies and vendors.
\item I redisegned the database from the previous system to suit the new requirements. Using OracleDB, PHP Codeigniter, Bootstrap, JQuery. Integrated with internal company SAP.
\end{tightitemize}
\sectionspace

% \runsubsection{ITS Training Center}
% \descript{| Programmer}
% \location{Jul 2017 – Feb 2018, Surabaya}
% \begin{tightitemize}
% \item Organize training and certification in ITS.
% \item Create CSS based on layout created by professional UI designer.
% \item Using MySQL and PHP Laravel as backend.
% \end{tightitemize}
% \sectionspace

\runsubsection{Pesantren Ramadhan}
\descript{| Programmer}
\location{Jul 2016 – Nov 2016, Surabaya}
\begin{tightitemize}
\item Will be used by over 300 users per day including student and teacher.
\item Active only 2 months per year, during Ramadhan.
\item Using MongoDB (sharded, scalable), NodeJS as backend, and ReactJS as frontend.
\end{tightitemize}
\sectionspace

\runsubsection{Internship Monitoring}
\descript{| Solo Programmer}
\location{Jul 2015 – Sep 2015, Surabaya}
\begin{tightitemize}
\item This app is only used by my local campus to monitor and evaluate student internships.
\item Using MySQL, PHP Laravel, Bootstrap, JQuery.
\item The application is currently running and maintained by campus.
\end{tightitemize}
\sectionspace

% \runsubsection{Guitar Chord Variation Finder}
% \descript{| Creator}
% \location{Jan 2017, Surabaya}
% \begin{tightitemize}
% \item I created this app using my knowloedge of music theory because of my interest in playing guitar and I found it hard to find variation of guitar chord.
% \item Using Coffeescript and ReactJS.
% \end{tightitemize}
% \sectionspace

%------------------------------------------------
% Awards
%------------------------------------------------

% \section{Awards}

% \begin{tabular}{rll}
% 2014 & top 52/2500 & KPCB Engineering Fellow\\
% 2014 & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
% \end{tabular}

% \sectionspace

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

\newpage % Start a new page
\begin{minipage}[t]{0.39\textwidth}

%------------------------------------------------
% Achievements
%------------------------------------------------

\section{Achievements}
\location{Aug 2018, Surabaya, Indonesia}
  Presenter of The 4th International Seminar on Science and Technology \\
\location{Apr 2017, Surabaya, Indonesia}
  Speaker on Laravel Training \\
\location{Jul 2015, Gorizia, Italia}
  Two gold medals and three silver medals at 54th International Choral Singing Competition Seghizzi 2015 \\
\location{Feb 2015, Bandung, Indonesia}
  One gold medal and one silver medal at ITB XXIV Choir Festival \\
\location{Feb 2014, Surabaya, Indonesia}
  2nd winner of Universitas Airlangga Choir Competition \\
\location{Sep 2013, Jakarta, Indonesia}
  Finalist (Top 20) Competitive Programming of Compfest, Universitas Indonesia \\
\sectionspace

%------------------------------------------------
% References
%------------------------------------------------

\section{References}
% \begin{tabular}{lll}
% \location{Handi Adiputra}
%   Senior Analyst in Accenture, Indonesia\\
%   +62 878-8152-1337\\
\location{Arianto Wibowo}
  Software Engineer in Shopee, Singapore\\
  +65 8590-2048\\
\location{Julio Antonius Leonard}
  Product Engineer in Go-Jek, India\\
  \href{mailto:julio.leonard@go-jek.com}{julio.leonard@go-jek.com}\\
\location{Hafiz Nuzal Djufri}
  Programmer Associate in Accenture, Indonesia\\
  +62 811-6658-910\\
\location{Eric Ivander Jeadi}
  Software Engineer in BukaLapak, Indonesia\\
  +62 896-7911-1735\\
\location{M Hilmy Fawwazy}
  UI Designer in Traveloka, Indonesia\\
  +62 853-3522-5791\\
% \end{tabular}

\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.59\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Organizational Experience
%------------------------------------------------

\section{Organizational Experience}

\subsection{Computer Engineering Student Association}
\location{Jul 2014 – May 2015}
  Steering Committee at student resource department HMTC \\
\location{Sep 2013 – Mar 2014}
  Organizing Committee at student resource department HMTC \\
\location{Feb 2013 – Dec 2014}
  Staff at National Programming Contest, Schematics \\
\location{Aug 2013 – Jul 2014}
  Staff at Entrepreneurship HMTC \\
\sectionspace

\subsection{ITS Student Choir}
\location{Aug 2014 – Aug 2015}
  Staff at Music Development Division \\
\location{Jan 2012 – Aug 2013}
  Training coordinator at "A Night to Remember" concert \\
\sectionspace

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{Undergraduate Thesis}
\descript{| Algorithm and Programming Lab}
\location{Software Design and Implementation of Flowchart Conversion into Problem Analysis Diagram for Source Code Generation}
Create a tool that can create and convert flowchart diagram into source code.
\sectionspace

\runsubsection{Master Thesis}
\descript{| Algorithm and Programming Lab}
\location{Development of Non-Interactive Searching Algorithm for Solving Ulam's Searching Problem with Many Lies}
Create an algorithm to solve a non-interactive Ulam searching problem with many lies. The algorithm results shows the best score on Sphere Online Judge.
\sectionspace

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
